---
title: "Benjamin From a Distance: Taking a Stroll Down *One-Way Street*"
author: "Jared Jameson"
date: "2023-04-29"
output:
  html_document: default
  pdf_document: default
---

## Introduction: Locating Benjamin

Walter Benjamin's book of aphorisms *One-Way Street* was one of two titles that he published in 1928, and those works stand today as the only two book-length projects Benjamin published during his short lifetime. The other 1928 publication, *The Origin of German Tragic Drama*, was Benjamin's failed habilitation, the equivalent of a dissertation for a PhD student in contemporary American education, which was originally intended to win him a position as a professional academic at the much vaunted Goethe University Frankfurt in Germany. To have it rejected, then, brought Benjamin's hopes for a career in academia to a screeching halt. However, despite his habilitation's failure in the eyes of the Frankfurt School's gatekeepers, as his first book, *Origins* shines as one of Benjamin's most commented on works, one considered requisite for any serious understanding of Benjamin's writing, one that has been the subject of in-depth analysis and interpretation far more so than its estranged counterpart *One-Way Street*. This is ironic in that the rejection of *Origins* by his intellectual peers served for Benjamin as a turning point where he would reinvent his style and theoretical bent with a much more radical flare, and *One-Way Street* was to be the book that announced this change in artistic direction. 

Benjamin's new artistic mode wasn't exactly ready-made for a widespread audience, though, as *One-Way Street* has often been viewed as a largely inaccessible, obtuse, and cryptic text that defies attempts at interpreting the sum of the various adjacent blocks of script printed on each page as a cohesive and uniform whole with connected and prescient themes. Benjamin scholar James McFarland, for example, writing in 2012 notes *One-Way Street* as "an avant-garde experiment involving sixty fragmentary and unorthodox texts, including everything from satirical lists to dreamprotocols to descriptions of children’s behavior, One-Way Street resists comprehension and so its exposition has languished."^1^ Though books of aphorisms were fairly common in the 20s when *One-Way Street* was published,^2^ Benjamin's esoteric, theoretical, and philosophical bents all seemed to permeate his writing in such a way that continually mystifies his reader to this day. 

*One-Way Street* is a radical book. One dedicated to, as the epigraph written on the books opening page plainly states, "Asja Lacis Street / after her who / as an engineer / cut it through the author."^3^ From the start, Benjamin poses *One-Way Street* not only as a collaborative effort by naming Lacis as its original architect but also as a monument to his intimate experience with a woman who so greatly impacted his life as to completely reconfigure the inner-most terrain of his identity. This clearly hints at the somewhat auto-biographical nature of the book, and perhaps offers a clue as to how the writing should be interpreted. It is no coincidence that Asja Lacis was also a Bolshevik communist that spurned an interest in communist ideology in Benjamin at a formative moment in his life. And Benjamin made it relatively clear in his writing that his interest in Lacis related directly to her politics. As McFarland puts it, "Benjamin considered his meeting with Asja Lacis to make epoch in his own existence, and his assessment of her significance . . . says nothing of her beauty but emphasizes her political character."^4^ The political nature of Benjamin's relationship to the woman he dedicated the book to strongly implies that the text of *One-Way Street* is politically charged and intended, in some ways, to function rhetorically as a type of propaganda for Benjamin's new found cause. Analyzing *One-Way Street* from this perspective, then, may also shed light on the historical moment that Benjamin inhabited. 

Previously, critical methodologies have lacked certain tools that might facilitate such a recontextualization, and in a digital era where maps, textual structures, and social networks can easily be visualized in new ways, the opportunity for a distant reading of Benjamin offers a new pathway to interpreting this text that has been so legendarily uninterpretable. These tools enable scholars to answer the call for radical new ways of "reading," since, as McFarland says, *One-Way Street* demands "readings  as  intrepid  as  its own  radical  posture."^5^ Specifically, the power of statistical analysis, which opens up the text to quantitative analysis, combined with the R programming language, which enables the plotting and visualizations of compiled data in various graphical forms, creates the opportunity to subject Benjamin's enigmatic *One-Way Street* to a round of textual analysis with the hopes that a distant reading of the text might produce new insights that can in turn lead to new or more robust interpretations of the book. **More precisely, the question driving this project is: How can programming languages like R, when employed as a tool for textual analysis, improve the experience of reading complicated texts like *One-Way Street* and lead to more satisfying and meaningful interpretations?** 

## Methodologies and Techniques: Using R to Mine Benjamin's sCrypt


### Building a Data Set / Corpus

To start this analysis of *One-Way Street*, the first step was to create the dataset, or the corpus, to be analyzed. This entailed, for one, the transcribing of *One-Way Street* into plain text files, one text file for each individual passage in the book. This was accomplished by first acquiring a digital .PDF version of the text, in this case the Edmund Jephcott and Kingsley Shorter translation from their collection *One-Way Street and Other Writings*.^6^ Then Adobe Acrobat was used to run optical character recognition (OCR), which started the process by making the text selectable and thereby transferrable into a plain text editor, in this case Note ++ was used to create the .txt files to make up the corpus. After OCR was completed, the text for the PDF was transferred over to a single text file, where the text was reviewed for any errors in the OCR process, of which there were many. Once these errors were corrected and the text accurately reflected the source material, the individual passages were copied into new text files and each saved individually with nothing but the text of the file, meaning the title was not included as part of the passage itself (although titles were recorded in the metadata file. More on that later). These files were saved in a directory titled "OWS-Benjamin." In total there were sixty-two files, including sixty individual passages; one file for the introductory epigraph that serves as the books dedication; and one file for the complete work, unseperated and titled. Once I had these files in a directory, I created a .zip file and uploaded that into a Github repository where it could be stored and later read into R Studio, the integrated development environment (IDE) for the R programming language, to create a more malleable dataframe. 


With the .txt files created, it was time to create the metadata file. This file consist of an Excel spreadsheet converted into a .csv file that contained all the relevant metadata associated with each individual passage. This is where information about the title, the year written, or the structural type is listed as supplementary info to foster the interpretations produced later. This file will also store results from counts and other analytical techniques that will be the building blocks for this projects final conclusions. Again, like with the text files, the finished .csv file was uploaded into a Github directory where it could then be read into R Studio for analysis.

### Pre-Processing the Corpus

```{r}
#First, the necessary libraries need to be loaded: 

library(tidyverse)
library(tidytext)
library(readtext)
library(widyr)
library(SnowballC)

#Next, the text files and metadata file need to be downloaded into the directory. The code used to do so is commented out below as it only needed to be run once:

#download.file("https://github.com/jaredsjameson/onewaystreet-archive/blob/4431b1538441327e1660bd7c700ddba366beefb9/OWS-Benjamin.zip?raw=true", "OWS-Benjamin.zip")

#Another bit of code unzips the compressed text files:

#unzip("OWS-Benjamin.zip")

OWS_Metadata <- read.csv("https://raw.githubusercontent.com/jaredsjameson/onewaystreet-archive/main/BenjaminW-OWS-metadata-Apr292023.csv")

file_paths <- list.files("OWS-Benjamin/")
OWS_texts <- readtext(paste("OWS-Benjamin/", file_paths, sep=""))

OWS_Benjamin_full <- full_join(OWS_Metadata, OWS_texts, by = c("Filename" = "doc_id"))

```
----------------------------------------------------

Now that the file has been joined and the metadata and texts are combined, it is time to start pre-processing the data. The first thing to do here is tokenize the data. First, the unnest_tokens() function will be used to separate the words and strip away punctuation.

----------------------------------------------------

```{r}


OWS_Benjamin_full.unnest.single <- OWS_Benjamin_full %>%
  unnest_tokens(word, text)
OWS_Benjamin_full.stop.single <- OWS_Benjamin_full.unnest.single %>%
  anti_join(stop_words)

OWS_Benjamin_full.unnest.sentences <- OWS_Benjamin_full %>%
  unnest_tokens(word, text, token = "sentences")

OWS_Benjamin_full.unnest.bigrams <- OWS_Benjamin_full %>%
  unnest_tokens(bigram, text, token = "ngrams", n = 2)
OWS_Benjamin_full.stop.bigrams <- OWS_Benjamin_full.unnest.bigrams %>%
  separate(bigram, into = c("first","second"), sep = " ", remove = FALSE) %>%
  anti_join(stop_words, by = c("first" = "word")) %>%
  anti_join(stop_words, by = c("second" = "word")) %>%
  filter(str_detect(first, "[a-z]") &
         str_detect(second, "[a-z]"))

OWS_Benjamin_full.unnest.trigrams <- OWS_Benjamin_full %>%
  unnest_tokens(trigram, text, token = "ngrams", n = 3)
OWS_Benjamin_full.stop.trigrams <- OWS_Benjamin_full.unnest.trigrams %>%
  separate(trigram, into = c("first","second", "third"), sep = " ", remove = FALSE) %>%
  anti_join(stop_words, by = c("first" = "word")) %>%
  anti_join(stop_words, by = c("second" = "word")) %>%
  anti_join(stop_words, by = c("second" = "word")) %>%
  filter(str_detect(first, "[a-z]") &
         str_detect(second, "[a-z]"))

OWS_Benjamin_full.stem.single <- OWS_Benjamin_full.stop.single %>%
        mutate(word_stem = wordStem(word))

```
Now pre-processing for this portion of the project is complete. The dataframes listed in the table below were produced by the above code and can be used for analysis:

Dataframe Title  | Dataframe Contents | Notes
------------- | ------------- | -------------
OWS_Benjamin_full.unnest.single  | 37925 obs. of 14 var. | Baseline, single word tokenized dataframe without stopword removal.
OWS_Benjamin_full.unnest.sentence  | 2193 obs. of 14 var. | Sentences separated for syntactical analysis without stopword removal. 
OWS_Benjamin.unnest.bigrams | 37863 obs. of 14 var. | Bigrams without stopwords removed
OWS_Benjamin.unnest.trigrams | 37801 obs. of 14 var. | Trigrams without stopwords removed
OWS_Benjamin_full.stop.single | 15498 obs. of 14 var. | Baseline, single word tokenized dataframe with stopwords removed.
OWS_Benjamin.stop.bigrams | 4997 obs. of 16 var. | Bigrams with stopwords removed.
OWS_Benjamin.stop.trigrams | 4980 obs. of 17 var. | Trigrams with stopwords removed.
OWS_Benjamin.stem.single | 15498 obs. of 15 var. | A word_stem column is added to the ...stop.single frame |
Reference Style Links and Images

Keeping the dataframes organized as allows cross-referencing and comparisons of the different versions of the same data. This way, if new questions arise as the work is progressing, each of these dataframes could be potential resources that can answer questions other versions may not be able to.

With these eight dataframes pre-processed, the discussion can inch on closer to the actual analysis of the text, but before getting there, an explanation of the techniques being applied to *One-Way Street* is in order.

### Techniques for Analysis: Basic Counting, Term Frequency, TF-IDF Analysis, and Co-Occurrrence

For this project, the various passages from *One-Way Street*, as they have been digitzed and formatted in the previous section, will be analyzed using basic counting, term frequency, Term Frequency-Inverse Document Frequency, and Topic Modeling. The ways in which these techniques are applied are detailed individually in the following sections.

#### Basic Counting
 
While the term *basic counting* may suggest something simplistic, the counting of items within different variables of the dataframes will give some good fundamental data that will be useful in not only structuring an argument for an interpretation of the text using quantitative data but also analyzing the structure and formal components of the language in the texts. By classifying the various forms that Benjamin uses for his aphoristic passages in *One-Way Street*, it becomes easier to assess the work aesthetically while being able ot clearly visualize the evidence. Each of the following counts will be added to a dataframe titled OBW_Benjamin_full.count variable., and then some visualizations will be created using the data.

The first and most obvious count to make is to count the words in eash separate passage. To do this the following code must be run:

```{r}
#OBW_Benjamin_full.count <- OBW_Benjamin_full %>%
 # mutate(words_count <- words %>%
 # group_by(source2, word) %>%
 # count()

  
OWS_Benjamin_full.unnest.single.groupcount <- OWS_Benjamin_full.unnest.single %>%
  filter(Title != "Complete Cycle") %>%
  group_by(Title, word) %>%
  count()
  
OWS_Benjamin_full.unnest.single.groupsum <- OWS_Benjamin_full.unnest.single.groupcount %>%
  group_by(Title) %>% 
  summarise(sum_title=sum(n), .groups = 'drop') %>%
  arrange(sum_title)
  

```

Now that there is a wordcount for each text stored in this variable, and it can be used in reference to any other questions later on. This data also works to help chart the number of passages that fall within certain wordcounts, meaning we can see how many shorter passages there are in relation to the other passages to get some broad level insight into the structure of *One-Way Street*.

First, the data needs to be grouped into how many titles fall within each range, for this project, we will look at consecutive ranges of fifty words. So, we will need a number for 1-50, 51-150 words, 151-300 words, 301-500 words, 501-1000, words, 1001-2000 words, 2001 words or more. These seven categories will function to make a quickly legible visualization that will put the the quality of length in *One-Way Streets* on display as a key structural element.The ranges above were chosen to represent a few different types of writing. The table below details:

Wordcount Range  | Type of Writing
------------- | -------------
0-50 | very short passsage or paragraph
51-150  | average size of a paragraph 
151-300 | lengthy paragraph or multiple short paragraphs
301-500 | multiple paragraphs, but shorter than an essay
510-1000 | short essay
1001-2000 | essay
2001+ | longest work

This information will serve as material for a visualization, but also as a key reference point for the rest of the analysis. A clearer picture of the groups within the text become visible, and further interpretation can fall back on this initial, seemingly simplistic data.

Below is the code to organize the data into groups according to range and a bar graph visualization of the presence of each range in the text.

```{r}
library(ggplot2)

OWS_Benjamin_full.unnest.single.agg.range <- OWS_Benjamin_full.unnest.single.groupsum %>%
  mutate(WordcountRange = case_when( sum_title > 0 & sum_title < 51 ~ "0001-0050",
  sum_title > 50 & sum_title < 151 ~ "0051-0150",
  sum_title > 150 & sum_title < 301 ~ "0151-0300",
  sum_title > 300 & sum_title < 501 ~ "0301-0500",
  sum_title > 500 & sum_title < 1001 ~ "0501-1000",
  sum_title > 1000 & sum_title < 2001 ~ "1001-2000",
  sum_title > 2000 ~ "2000+"))

OWS_Benjamin_full.length.agg.range <- OWS_Benjamin_full.unnest.single.agg.range %>%
  group_by(WordcountRange) %>%
  count(WordcountRange) %>%
  arrange(WordcountRange)
  
  
head(OWS_Benjamin_full.length.agg.range)

```


Visualize the above data as a bar graph will display how *One-Way Street* is divided in terms of passage length. Here is the code for that:


```{r}
OWS_Benjamin_full.length.agg.range.bgraph <- ggplot(data=OWS_Benjamin_full.length.agg.range, aes(x=WordcountRange, y=n, fill = WordcountRange)) +
  geom_bar(stat = "identity", color = "black") +
  geom_text(aes(label=n), vjust=1.6, color="black",
            position = position_dodge(0.9), size=3.5) +
  labs(y= "Number of Texts per Range", x = "Wordcount Ranges")
  


OWS_Benjamin_full.length.agg.range.bgraph +scale_fill_brewer(palette="Dark2")
```

This graph identifies a clear sweet spot in terms of length in *One-Way Street* is between 50 and 300 words. In fact, that number accounts for exactly 75% of the total number of passages falling in that range. This suggests that a closer look into any of three main characteristic lengths, the uncharacteristically short less than 50 words group, the characteristic standard 51-300 words group, and the uncharacteristically long 301-2000 words group (the longest work is just over 2000 words). Isolating each of these groups for later comparative analysis may be useful later. 

Delineating the text this way may also be a way to support some of the argument suggesting the the longest passage in *One-Way Street*, "Imperial Panorama," functions somehow as he core or heart of the text. The arguments for this largely rely on the fact that Imperial Panorama was one of few texts written earlier than the 1925-26 window that the rest of the text was written in. Mcfarland, for example says that Imperial Panorama was "the 'original' aphorism in the collection, KAISERPANORAMA," which he perceives the rest of the passages extending from as a sort of "encounter from various directions motifs of space, of dream, of gambling, of rupture and of loss. They demonstrate the earlier tendencies in Benjamin’s thought  that break into expression in the book." McFarland sees this as a model for "Benjamin’s further work, in particular the affinity between Asja Lacis Street and theParisian arcades Benjamin explored for the rest of his life."^7^ This analysis of *One-Way Street* then already finds connections to other theory's of Benjamin's work and shows promise for further development. Perhaps another visualization will strengthen this case.

In addition to length, the metadata also includes a column designating different formats that each passage models. There are 14 individual formats that the passages in *One-Way Street* adhere to, and by taking a closer look at these and producing a visualization of how many passages exhibit each different format, further structural insights can be gained.

```{r}
OWS_Metadata.formatadj <- read.csv("https://raw.githubusercontent.com/jaredsjameson/onewaystreet-archive/main/BenjaminW-OWS-typeadj-metadata-Apr292023.csv")

OWS_Metadata.groupform <- OWS_Metadata.formatadj %>%
  filter (Title != "Complete Cycle") %>%
  group_by(Format) %>%
    count(Format) %>%
  arrange(n) 


OWS_Metadata.groupform.bgraph <- 
  ggplot(data = OWS_Metadata.groupform, aes(x = Format, y = n, fill = Format)) +
  geom_bar(stat = "identity", color = "black", show.legend = FALSE) +
  geom_text(aes(label=n), vjust=0.4, hjust=1.5, color="black",
            position = position_dodge(0.9), size=2.5) +
  labs(y= "Number of Texts in Format", x = "Formats") +
  coord_flip() +
  theme(legend.position="bottom")

OWS_Metadata.groupform.bgraph
  
```


The above bar graph highlights how key the single paragraph format is to *One-Way Street*, as it eclipses all other forms in comparison comprising a total of just under 50% of the work. Add to that fact the sum of the other two highest occuring formats, subtitled sections" and "unlabeled sections," which both had eight and nine occurences respectively, totaling 17, making up another roughly 29% of the text, So out of the original total of fourteen different formats, these three, "single paragraphs," "subtitled sections," and "unlabeled sections," dominate 79% of the book. 

This look at the structure of the text, after being visualized in this way, helps shape a solid aesthetic interpretation of the text, but it also helps the observant analyst pinpoint what might be missing. Here, there is one other means of categorizing the texts structure that could add to the above 2 visualizations depiction of Benjamin's writing. That is, like McFarland points out, Benjamin's writing in *One-Way Street" often exhibits certain qualities like being dream-centered, satirical, or child-themed.^8^ And I would add further categories like romantic, political, architectural to name a few. This type of classification is beyond the scope of this project, but it is example of just the type of idea that might add dimension to an interpretation that might be lost without the aid of visualizing the other data and reflecting on the findings.

#### Term Frequency

With the above basic counting now complete, it is time to move on to more advanced techniques such as term frequency. 

```{r}
OWS_Benjamin_full.single.termfreq <- OWS_Benjamin_full.stop.single %>%
  filter(Title != "Complete Cycle") %>%
  group_by(Title, Format) %>%
  count(Title, word, sort = T)  %>%# count occurrence of word and sort descending
  group_by(Title) %>% 
  mutate(n_tot = sum(n), # count total number of words per doc
         term_freq = n/n_tot) %>%
  arrange(desc(term_freq))

head(OWS_Benjamin_full.single.termfreq)
```
Peaking at the data, the term with the highest frequency is "wake," with a term frequency of 0.33. This is especially compelling considering that this term derives from the passage titled "Closed for Alterations," which is about a hotel room being "closed for alterations" after its tenant committed suicide by gunshot to the head.^9^ This particular passage has always been a memorable one for readers also because of Benjamin's own suicide. This early echo of the author's impending doom certainly has a weight to it already, so perhaps it should not be surprising that it's use of "wake" is the highest listed, although it is tied with three other terms: "conception," "conquer," and  "convince." These terms all share the 0.33 term frequency rating. All three terms are from the passage "For Men,"^10^ and they are all related in certain ways to the term "wake," at least from a standpoint of common association. For instance to wake is regain consciousness after sleep, to become aware again, and a conception not only marks the arriving at the formation of a concept, but also a birth, into the new day. The word *conquer* is commonly associated with waking in relation to phrases like "seize the day," "early bird catches the worm," "Up and at 'em," etc. And to *convince* is to *wake* someone up to a point-of-view or belief. Is this the type of "waking" that emanates from Benjamin's writing here? 

Of course, the passages "Closed for Alterations" and "For Men" both are among the shortes in *One-Way Street*, and among the four total terms tied for term frequency, *wake* is the only one that actually appeared more than once its passage. That's right, the other three terms from "For Men" only show up once, but their frequency is incredibly high because there are only three other words in the passage after accounting for stop words. The entire passage, in fact, is only one sentence. This strengthens the case for *wakes* more legitimate frequency rating, but it also suggests that a better indication of term frequency might be gotten by (1) filtering out terms that only appear once in a text and (2) filtering out those texts that are incredibly short and thereby might be skewing frequency readings. Luckily, we can eliminate those texts based on the early analysis that broke those groups down. 

For now, the data will be filtered for terms that occur at least twice.

```{r}

OWS_Benjamin_full.single.termfreq.filtered <- OWS_Benjamin_full.single.termfreq %>%
  filter(n > 1)
head(OWS_Benjamin_full.single.termfreq.filtered)

```


Drilling down a bit further now, by the adjusted frequency ratings, the top term is still *wake*, but now the second highes term frequency is 0.25, deriving from the word *street*. Of course, it is not surprising at all that in a book titled *One-Way Street* that the term *street* would be one with a high frequency, but when paired with the frequency of the word *wake*, the combination offers fodder for interpretation. 

The street is in fact a wake, in the sense that the street's progress forward in its construction cut into the earth and tore a wide swath through it for travelers to follow behind in, led by the roadways into the worlds of the men who build them. To be in the *wake* of the roadway is to be on the street, walking, lagging behind but pushing ahead as the present instant unfolds. Benjamin was well-known for his celebrating the Baudelairian figure of the flaneur, the aimless dandy wanderer who takes in the city for what it is only by walking through its streets. *Waking* life is to venture back out from slumber, the dream world, and back into the world again to carry on with life. This type of interpretation can add to our overall criticism of the shorter pieces that seem to enhance the affect on the reader of term frequency. 

Still, though, it seems that the data needs to be refined further. After all, the earlier analysis of wordcount groupings resulted in the statement that over 75% of the passages in *One-Way Street* have wordcounts in between 50 and 300. Accomodating for this might help uncover more meaningful instances of term frequency in relation to our previously established word count range findings.


```{r}
OWS_Benjamin_full.single.termfreq.filtered.lengroup <- OWS_Benjamin_full.single.termfreq.filtered %>%
  filter(n_tot > 30 & n_tot < 225)


head(OWS_Benjamin_full.single.termfreq.filtered.lengroup)

```

Both the top terms here derive from the same passage, interestingly, one titled "No. 13." Again, strangely enough, the terms *books* and *harlots* showing the highest term frequencies among passages in this wordcount range, is not surprising, as Benjamin's writing, including that of *One-Way Street*, often references his fondness for both collecting books and visiting prostitutes. From an interpretive point of view, the term *harlot*, though, in relation to the term *books* oddly clashes with the epigraph from the book's opening dedication to his romantic interest Asja Lacis. The question arises as to why mention *harlots* so frequently, so strongly here in a book supposedly inspired by her. It is also interesting that these high occurrence and high frequency terms show up here, in "No. 13," as the number 13 reverberates through many of the other pieces in *One-Way Street*, and Benjamin is known to have studied the Kabbalah which has sacred numerological components to its teachings. 

Another interesting outcome from the term frequency analysis is the third term on the list *dream*. Here, there could be connections drawn toward *wake* from the earlier, shallower term frequency analysis, which could create further support for an interpretation of the importance of dreams and the liminal ambiguities between sleeping and waking states that seem of central importance here. In this case, the term derives from the second passage in the book, "Breakfast Room."^11^ Benjamin's use of *dream* here at such a high frequency is effective, as it resonates throughout the reading from the very beginning, serving to almost prime reader's attunement to the dreamlike qualities spread throughout the work. 

The terms found here in this term frequency analysis do add depth to interpretive efforts by both sparking the above developed ideas and serving as evidence later once a full interpretation has been crafted. This technique seems to be useful for pointing toward the themes of texts as assessed from different levels. The statements here are made rather hesitantly though, as a deeper understanding of term frequency relevance is needed to better understand the results and how much weight should be attributed to them. Term frequency as a tool for textual analysis also seems like it is most effective when used with other basic counts of term occurence.

Lastly, drilling down further might help offer more interesting and useful results, and the format categories categories established earlier have yet to be considered in terms of term frequency. Since we now that the single paragraph is the most dominant format in *One-Way Street*, it makes sence to look at this area as well. The below code does just that:


```{r}
OWS_Benjamin_full.single.termfreq.filtered.parlengroup <- OWS_Benjamin_full.single.termfreq.filtered.lengroup %>%
  filter(Format == "single paragraph") %>% 
  arrange(desc(term_freq))

head(OWS_Benjamin_full.single.termfreq.filtered.parlengroup)

```
This dataframe shows which terms have the highest frequency for all passages in *One-Way Street* that are of the commonest length of more than 50 and less than 300 words and in the commonest format, the single paragraph. Here, *dream* takes the number one spot with the highest frequency of approximately 0.08. At this length, the intensisty of the frequencies are drastically lower than they were in the previous examples. This exemplifies the relationship of term frequency to the length of a passage quite nicely, where the shorter a passage is the more weightier each word in it becomes. This seems obvious but becomes interesting when critically examining Benjamin's aesthetic choices. In that case, the argument could be made that by choosing such a short medium in the single paragraph, Benjamin not only lends each of his words a more powerful, more resonant frequency, although only at a short burst. In addition to this, by sandwiching occasional longer passages between these sporadic bursts of paragraphs, Benjamin lends those longer passages a certain sense of gravitas, a seeming immensity, to these passages. These longer works are only "longer" in the context of the other writings in *One-Way Street*, outside of this text, these passages are relatively short themselves, with the absolute longest of them being, as earlier mentioned, only around 2,000 words. Compared to even a "short" novel, this is still pretty short, but in Benjamin's little book, these passages stand out like giants and demand attention more than they ortherwise would. 

Outside of this formal analysis, though, this list does provide interesting insights, with the top five terms, *dream*, *secret*, *streetcar*, *children*, and *world*, all seeming to reflect key themes that recur throughout the bok. It will be interesting to look back at this in conjunction with the later topic modeling in this project. But before that, perhaps visualizing the difference in term frequency intensity in shorter works will help bring that point home:


```{r}
OWS_Benjamin_full.single.termfreq.filtered.stackedgroups1 <- data.frame(append(OWS_Benjamin_full.single.termfreq.filtered, c(StackedClass="All Formats"), after = 2))


OWS_Benjamin_full.single.termfreq.filtered.stackedgroups2 <- data.frame(append(OWS_Benjamin_full.single.termfreq.filtered.parlengroup, c(StackedClass="single par."), after = 2))

OWS_Benjamin_full.single.termfreq.filtered.stackedgroups.whole <- rbind(OWS_Benjamin_full.single.termfreq.filtered.stackedgroups1, OWS_Benjamin_full.single.termfreq.filtered.stackedgroups2)

OWS_Benjamin_full.single.termfreq.filtered.stackedgroups.stackedready1 <- OWS_Benjamin_full.single.termfreq.filtered.stackedgroups.whole %>%
  filter(term_freq >= 0.081761006)

OWS_Benjamin_full.single.termfreq.filtered.stackedgroups.stackedready2 <-
  OWS_Benjamin_full.single.termfreq.filtered.stackedgroups.whole %>%
  filter(StackedClass == "single par.")
 

OWS_Benjamin_full.single.termfreq.filtered.stackedgroups.stackedready3 <- 
  OWS_Benjamin_full.single.termfreq.filtered.stackedgroups.stackedready2 %>%
   filter(term_freq <= 0.077669903 & term_freq >= 0.054545455)

OWS_Benjamin_full.single.termfreq.filtered.stackedreadywhole <-  rbind(OWS_Benjamin_full.single.termfreq.filtered.stackedgroups.stackedready1, OWS_Benjamin_full.single.termfreq.filtered.stackedgroups.stackedready3)



OWS_Benjamin_full.single.termfreq.stackedbgraph <- 
  ggplot(data = OWS_Benjamin_full.single.termfreq.filtered.stackedreadywhole, aes(x = StackedClass, y = term_freq, fill = word, color = "black")) +
  geom_bar(stat="identity") 
  
 

OWS_Benjamin_full.single.termfreq.stackedbgraph




```
This visualization highlights clearly the differing levels of frequency as works shorter than a paragraph are taken out of the data pool. This visualization shows how certain words resonate more strongly in the text, at least according to the current method of calculation. This can be enhanced.


### TF-IDF 

The term frequency above yielded some interesting results, but still, there is more in terms of frequency that we can learn about *One-Way Street*. To go further, the technique of Term Frequency - Inverse Document Frequency will be explored as a tool for analysis. Ph.D and author Faith Karabiber defines term frequency as "a widely used statistical method in natural language processing and information retrieval. It measures how important a term is within a document relative to a collection of documents (i.e., relative to a corpus)." ^12^ This techniques should help to verify or invalidate the previous findings. The below codes begins that TF-IDF analysis of *One-Way Street*.

```{r}
OWS_Benjamin_full.stop.single.tdidf <- OWS_Benjamin_full.stop.single %>%
  count(Title, Format, word, sort = TRUE) %>%  
  bind_tf_idf(word, Title, n) %>%
arrange(desc(tf_idf))


head(OWS_Benjamin_full.stop.single.tdidf) 
```

Immediately, the changes in the ratings of the word relevances are apparent. In the earlier term frequency analysis the first four words, *wake*, *conception*, *conquer*, and *convince* are all still in place, although the order of  these words in the TD-IDF analysis has changed. *Conception*, *conquer*, and *convince*, though, in the TD-IDF have different frequencies, whereas in the earlier analysis they were tied. This offers more dimension and support to that earlier analysis as it helps differentiate between of these three important terms. The consistent presence of wake here helps support the earlier arguments arrived at initially and adds a bit of nuance to the position. However, not every change here supports initial thoughts on the earlier term frequency analysis results.

The fifth spot on the list of the original term frequency analysis was *street*, which in the TD-IDF analysis here, has been replaced by *knowing*. *Knowing* here moves against earlier interpretations of *street*'s relationship to *wake*, but it suggests interesting connections on its own. However, it is interesting that street is missing here, and following that path might help reinforce the now-in-doubt earlier interpretation. Drilling down with the same filters from the earlier analysis will give us more data to compare. 

```{r}
OWS_Benjamin_full.stop.single.tdidf.filtered <- OWS_Benjamin_full.stop.single.tdidf %>%
  filter (n > 1) %>%
arrange(desc(tf_idf))

head(OWS_Benjamin_full.stop.single.tdidf.filtered)
```

Oddly enough, when filtering the data to account for only words that are used more than once, *street* retakes its place on the list. Perhaps the earlier interpretation wasn't far off after all, and those first TD-IDF results 



```{r}


OWS_Benjamin_full.tdidf.filtered.par <- OWS_Benjamin_full.stop.single.tdidf.filtered %>%
  filter(Format == "single paragraph") %>%
arrange(desc(tf_idf))

head(OWS_Benjamin_full.tdidf.filtered.par)
```
Here, filtering to only account for the single paragraph format passages changes the ranings yet again. *Wake* seems unshakable from the top, but *street* is now replaced with *passed*. At this point, the R console that processed this data begins to look like a Ouija board. How? By bringing these four words to the surface of *One-Way Street*--*wake*, *street*, *knowing*, and *passed*, with *knowing* and *passed* both being the terms that interchanged with *street*'s rank in the frames--it's as if the book speaks, telling us that "knowing streets wakes what passed through them before through the perception of what was left behind. This is precisely the contradictory, reflexive type of language that Benjamin is often admired for, and it is striking how the analysis becomes both deconstructive and generative.  


### Co-Occurence

Co-Occurence analysis could help solve the problem. See the code below for that:

```{r}
library(widyr)

OWS_Benjamin_full.wordpairs <- OWS_Benjamin_full %>% 
  mutate(passage_end = word(text, -5000, end = -1)) %>% # extract last 100 words
unnest_tokens(word, passage_end) %>% # tokenize
filter(!word %in% stop_words$word) %>% # remove stopwords
pairwise_count(word, Title, sort = TRUE, upper = FALSE)


head(OWS_Benjamin_full.wordpairs)

```

Immediately, one thing that sticks out here is the term *life*, which was not prominent in our other frequency ratings, but here it shows up in the top four wordpair occurrences. As interesting as this is, it will be more interesting to filter this list to look for occurences of street and the words it pairs with to help answer the earlier arrived at interpretive questions. 


```{r}
OWS_Benjamin_full.wordpairs.streetfiltered <- OWS_Benjamin_full.wordpairs %>% 
  filter(item1 == "street" | item2 == "street" )

OWS_Benjamin_full.wordpairs.streetfiltered3s <- OWS_Benjamin_full.wordpairs.streetfiltered %>%
  filter(n == 3)

OWS_Benjamin_full.wordpairs.streetfiltered3s

```

Thats 1920 words paired with street. Visualizing this data as a network graph might bear interesting results. The below network graph shows all co-occurences that take place with street at least 3 times, which was the most that any pair occurred.  

```{r}
library(igraph)
library(ggraph)

OWS_Benjamin_full.wordpairs.streetfiltered.netgraph <- OWS_Benjamin_full.wordpairs.streetfiltered3s %>% 
   graph_from_data_frame() %>% 
ggraph(layout = "fr") +  # place nodes according to the force-directed algorithm of Fruchterman and Reingold
geom_edge_link(aes(edge_alpha = n, edge_width = n), edge_colour ="orange") + 
  geom_node_point(colour = "purple", size = 5) + 
  geom_node_text(aes(label = name), repel = TRUE, point.padding = unit(0.2, "lines")) +
   theme_void()
 
 OWS_Benjamin_full.wordpairs.streetfiltered.netgraph
```

These are compelling associations, but I do not see much to support our interpretation about the term *street*'s relationship to the term *wake*. Perhaps looking at the network for co-occurrences of wake can shed light on this issue. 

```{r}
OWS_Benjamin_full.wordpairs.wakefiltered <- OWS_Benjamin_full.wordpairs %>% 
  filter(item1 == "wake" | item2 == "wake" )

OWS_Benjamin_full.wordpairs.wakefiltered2s <- OWS_Benjamin_full.wordpairs.wakefiltered %>%
 filter(n == 2)

OWS_Benjamin_full.wordpairs.wakefiltered2s

```

Here, wake doesn't have as many recurring pairs as street, but there are still some interesting reslts with *wake* $ *street* showing up here together at number five on the list. However, the wake-street pair only has one recurrence, which means it isn't necessarily as relevant here as word pairs with more recurrences. Even though this network is small, a visualization still may help put things into perspective.


```{r}

library(igraph)

 OWS_Benjamin_full.wordpairs.wakefiltered.netgraph <- OWS_Benjamin_full.wordpairs.wakefiltered2s %>% 
   graph_from_data_frame() %>% #convert to graph
ggraph(layout = "fr") +  # place nodes according to the force-directed algorithm of Fruchterman and Reingold
geom_edge_link(aes(edge_alpha = n, edge_width = n), edge_colour =
"purple") + geom_node_point(colour = "orange", size = 5) + 
  geom_node_text(aes(label = name), repel = TRUE, point.padding = unit(0.2, "lines")) +
   theme_void()
 
 OWS_Benjamin_full.wordpairs.wakefiltered.netgraph

```
Interestingly enough, that term *life*, noted as the most frequent with co-occurences shows prominently here, almost apart from all the other terms. This will add even more to the interpretation if there are visualizations for those other two words that replaced street in certain frequency counts, as mentioned earlier: *knowing* and *passed*.

```{r}
OWS_Benjamin_full.wordpairs.knowingfiltered <- OWS_Benjamin_full.wordpairs %>% 
  filter(item1 == "knowing" | item2 == "knowing" )

#OWS_Benjamin_full.wordpairs.wakefiltered2s <- OWS_Benjamin_full.wordpairs.wakefiltered %>%
 #filter(n == 2)

OWS_Benjamin_full.wordpairs.knowingfiltered

```

```{r}
library(igraph)

 OWS_Benjamin_full.wordpairs.knowingfiltered.netgraph <- OWS_Benjamin_full.wordpairs.knowingfiltered %>% 
   graph_from_data_frame() %>% #convert to graph
ggraph(layout = "fr") +  # place nodes according to the force-directed algorithm of Fruchterman and Reingold
geom_edge_link(aes(edge_alpha = n, edge_width = n), edge_colour =
"gold") + geom_node_point(colour = "blue", size = 5) + 
  geom_node_text(aes(label = name), repel = TRUE, point.padding = unit(0.2, "lines")) +
   theme_void()
 
 OWS_Benjamin_full.wordpairs.knowingfiltered.netgraph
```


Here, the stark nature of the results is actually compelling. *Knowing* has a high term frequency in certain passages, high enough to displace the word *streets* in certain instances from the high frequency lists. The fact that this knowing is paired so nicely with these three things gives some depth to how it might be interpreted in the group: knowing, street, passed, and wake. Lastly, lets look at passed and see what it is most connected to.



```{r}
OWS_Benjamin_full.wordpairs.passedfiltered <- OWS_Benjamin_full.wordpairs %>% 
  filter(item1 == "passed" | item2 == "passed" ) %>%
filter(n == 3 | n ==4)

#OWS_Benjamin_full.wordpairs.wakefiltered2s <- OWS_Benjamin_full.wordpairs.wakefiltered %>%
 #filter(n == 3 | n ==4)

OWS_Benjamin_full.wordpairs.passedfiltered
```
```{r}
OWS_Benjamin_full.wordpairs.passedfiltered.netgraph <- OWS_Benjamin_full.wordpairs.passedfiltered %>% 
   graph_from_data_frame() %>% #convert to graph
ggraph(layout = "fr") +  # place nodes according to the force-directed algorithm of Fruchterman and Reingold
geom_edge_link(aes(edge_alpha = n, edge_width = 5), edge_colour =
"blue") + geom_node_point(colour = "yellow", size = 5) + 
  geom_node_text(aes(label = name), repel = TRUE, point.padding = unit(0.2, "lines")) +
   theme_void()
 
 OWS_Benjamin_full.wordpairs.passedfiltered.netgraph
```

```


This visualization brings a new word into the fray *hand*, which is very strongly tied to the word passed here. Of course, this is fairly common sensical in that the hand is generally used to pass things, so the association is not surprising at all. But, in the context of *One-Way Street*, it is somewhat compelling in that the act of things changing hands is not something commonly brought up when considering Benjamin's work, but the concept of the *gift* is, which could be related. All in all, these terms seem compelling enought to inspire furether research.


## Conclusion

Benjamin's work is characteristically enigmatic and *One-Way Street* is no different. But, with textual analysis techniques and visualizations of his work, new solutions to his prose puzzles become apparent. This work started with a very broad research question: Could the R programming language, quantitative analysis, and data visualization help build new interpretations of Walter Benjamin's unorthodox book *One Way Street*? The answer, unsurprisingly, was a resounding yes, however, the ways in which this analysis was used in this work to derive interpretations, I think, is much different than how these types of datapoints are normally used. Along the way, the broad question this work began with fertilized the ground for more specific questions to pop up along the way. Revising the text this way was like a journey, in fact, to state it quite boldly, a new way of reading. The idea springs to mind that this type of visualization of texts should be built in to electronic books in ways that it currently is not. If it were, though, this kind of  reading, a form of distant but active reading, proides a really rewarding experience in cases where the reader is already familiar with the text he or she is reading and already interested in analyzing the text for some purpose. This is exactly what I think Benjamin himself would like about this type of analysis, as much of his work, including *One-Way Street* was written specifically to shake up the way people read through and think about and interact with a book. In this case, I do think there were interesting insights that I was able to latch onto that I wouldn't have been able to otherwise identify, and providing evidence for those interpretations as well as inspiration for direction to take them in was easy and intuitive. 

Through this reading several interesting things came to light, the most interesting of which being the connections between the term street, one central to the book, to the ideas of dreaming and waking. While dreaming and waking as themes are apparent just throgh reading *One-Way Street* it doesn't seem as prominent when reading as it actually is in the text according to this analysis. In addition, the word passed, being strongly related to both street and wake, is more compelling here than may initially seem, as *The Arcades Project*



## End Notes


1. McFarland, “Setting the Stage," 212.

2. Scholem cited in a footnote in Sontag, Introduction, 19. 

3. Benjamin, *One-Way Street*, 45.

4. McFarland, "Setting the Stage," 214.

5. McFarland, "Setting the Stage," 215.

6. This version was first published in 1978 as the first English traslation of the full cycle of writing that made up the original German version, *Einbahnstraße*. Benjamin, Walter. *One-Way Street*.

7. McFarland, "Setting the Stage," 215-16.

8. McFarland, "Setting the Stage," 212.

9. Benjamin, *One-Way Street*, 91.

10. Benjamin, *One-Way Street*, 47.

11. Benjamin, *One-Way Street*, 45.

12. Karabiber, "TF-IDF."




## Bibliography

Benjamin, Walter. *One-Way Street*. *One-Way Street and Other Writings*, trans. Edmund Jephcott and Kingsley Shorter. NLB, 1979.

Benjamin, Walter. *The Origins of German Tragic Drama*. Verso, 1998.

McFarland, James. “Setting the Stage: An Introduction to One-Way Street.” In The Germanic Review: Literature, Culture, Theory, 87, no. 3, (2012): 211-216. DOI: 10.1080/00168890.2012.707939.

Karabiber, Faith. "TF-IDF — Term Frequency-Inverse Document Frequency." Learn Data Sci, https://www.learndatasci.com/

Sontag, Susan. Introduction. In *One-Way Street and Other Writings*, trans. Edmund Jephcott and Kingsley Shorter. NLB, 1979.